Security Metrics for the Android Ecosystem

### 2015-07-23 security_scoring.tex
Deployment to at least 1% is reasonable but arbitrary

We can compute the uncertainty for $f$, $u$ and $m$.
$f$ is computed by taking the total secure device days and dividing it by the total insecure and secure device days.
The total secure device days and total insecure device days are both counting experiments and so their measurement error is their square root~\cite{Taylor1997}.
Since the numbers involved are large, the uncertainty in $f$ is small.
$u$ is computed by taking the sum of the proportions of devices running the most recent version each day, both the count of devices running the maximum version and total count have square root uncertainties.
$m$ is computed by counting the number of vulnerabilities which affected that entity and which have not yet been fixed on any device we have observed from that entity every day and averaging over observed days.
However, it could be that the entity has released a fix to some devices but we have not yet observed a device with that fix.
So the uncertainty in each vulnerability truly being outstanding is the probability of not having observed a fixed device if a fixed device existed.
We assume that if the fix has been released then at least \daMeanOutstandingProbability\ of devices have the fix.
This gives an uncertainty of \daMeanOutstandingUncertaintyEquation\ where $n$ is the number of devices contributing to that day's data for each vulnerability outstanding each day.
The Python \texttt{uncertainties} library was used to propagate uncertainties through calculations.
This does not capture systematic errors such as those due to not including vulnerabilities which do affect devices, but for comparison that does not matter.
However, we do not include manufacturer specific vulnerabilities that will influence comparisons, but we expect that performance in fixing manufacturer specific vulnerabilities is strongly correlated with performance fixing vulnerabilities affecting all of Android.

>>>>

We can compute the uncertainty for $f$, $u$ and $m$.
$f$ is computed by taking the total secure device days and dividing it by the total insecure and secure device days.
The total secure device days and total insecure device days are both counting experiments and so their measurement error is their square root~\cite{Taylor1997}.
Since the numbers involved are large, the uncertainty in $f$ is small.
$u$ is computed by taking the sum of the proportions of devices running the most recent version each day, both the count of devices running the maximum version and total count have square root uncertainties.
$m$ is computed by counting the number of vulnerabilities which affected that entity and which have not yet been fixed on any device we have observed from that entity every day and averaging over observed days.
However, it could be that the entity has released a fix to some devices but we have not yet observed a device with that fix.
So the uncertainty in each vulnerability truly being outstanding is the probability of not having observed a fixed device if a fixed device existed.
We assume that if the fix has been released then at least \daMeanOutstandingProbability\ of devices have the fix.\footnote{The selection of \daMeanOutstandingProbability\ is arbitrary, but if a version has only been deployed to a smaller proportion then it does not have a substantial penetration.}
This gives an uncertainty of \daMeanOutstandingUncertaintyEquation\ where $n$ is the number of devices contributing to that day's data for each vulnerability outstanding each day.
The Python \texttt{uncertainties} library was used to propagate uncertainties through calculations.
This does not capture systematic errors such as those due to not including vulnerabilities which do affect devices, but for comparison that does not matter.
However, we do not include manufacturer specific vulnerabilities that will influence comparisons, but we expect that performance in fixing manufacturer specific vulnerabilities is strongly correlated with performance fixing vulnerabilities affecting all of Android.
